The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-11-27 article.tex
@richelbilderbeek suggests to use MBD and BD, instead of 0 and 1
Add hypthesis, progress https://github.com/richelbilderbeek/razzo/issues/143

@@

\item So far we have simulated two datasets of trees under the two models: 
$\{T_{i}^{BD}\}_{i=1}^{N_{S}}$ and $\{T_{i}^{MBD}\}_{i=1}^{N_{S}}$.
We used them to generate a dataset of alignments for each model: $\{X^{BD}_{i}\}_{i=1}^{N_{S}}$ and $\{X^{MBD}_{i}\}_{i=1}^{N_{S}}$. From each dataset we produced a posterior distribution from a BD prior: 
$P_{i}(\theta | X^{BD}_{i}, BD)$ and $P_{i}(\theta | X^{MBD}_{i}, BD)$.
\gio{
  1) We might want to rename the models, e.g. BD = (0) and MBD = (1). These names with capital letters are too big and ugly;
}

>>>>

% Hypothesis: general
\item We hypothesize that the error made today, using BD tree priors,
increases with an increased number or stronger effect of multiple birth events.
This is straightforward: without multiple birth events or such event having
no effect, the MBD model falls back to a BD model. We expect larger
errors when we deviate more from the BD model's assumptions.

\item Additionally, we hypothesize MBD having a stronger effect if the normal
speciation process is less pronounced. The more speciations are caused by the
BD process, there are relatively less multiple-birth events.

\item We expect the effect of extinction rates to be neutral, as extinctions will
hit lineages created by both speciation processes equally.

\item Summarized, we expect the error made be correlated to the number 
of species created by the multiple-birth process over the total number 
of species created:

\begin{equation}
<e> = f(\frac{n_{taxa}^{MBD}}{n_{taxa}^{BD} + n_{taxa}^{MBD}})
\end{equation}

Where $<e>$ denotes the expected error, $f$ is a monotonously increasing 
function of unknown shape, $n_{taxa}^{MBD}$ is the number of taxa created
in multiple-birth events and $n_{taxa}^{BD}$ is the number of taxa created
by the standard BD specition process.

@@

\subsection{Measuring the inference error}

\item So far we have simulated two datasets of trees under the two models: 
$\{T_{i}^{BD}\}_{i=1}^{N_{S}}$ and $\{T_{i}^{MBD}\}_{i=1}^{N_{S}}$.
We used them to generate a dataset of alignments for each model: $\{X^{BD}_{i}\}_{i=1}^{N_{S}}$ and $\{X^{MBD}_{i}\}_{i=1}^{N_{S}}$. From each dataset we produced a posterior distribution from a BD prior: 
$P_{i}(\theta | X^{BD}_{i}, BD)$ and $P_{i}(\theta | X^{MBD}_{i}, BD)$.
\gio{
  1) We might want to rename the models, e.g. BD = (0) and MBD = (1). 
  These names with capital letters are too big and ugly;
}
\richel{
  I would strongly prefer MBD and BD, as I feel replacing the big ugly 
  capital letters by short pretty numbers hurts readability even more 
}
